251 MA

### 2023-02-07 code/process.Rmd
various tweaks

parse_t <- function(tval, within_between) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pt(q=val, df=df, lower.tail=FALSE)*2
  d_calc=NA
  N_from_df=NA
  if(within_between=="between"){
    d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
    N_from_df=df+2 # between so add 2
  }
  else{
    d_calc=val/sqrt(df)
    N_from_df=df+1
  }
  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "beta"=NA, "SE"=NA))
}
```

```{r}
parse_f <- function(fval, within_between){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
  d_calc=NA
  N_from_df=df_1+df_2+1
  if(!is.na(df_1)&&df_1==1){
    if(within_between=="between"){
      d_calc=2*sqrt(val)/sqrt(df_2) # if there's just two groups, then F=t**2 and we can use the t-test thingy
    }
    else{
      d_calc=sqrt(val)/sqrt(df_2)
    }
  }
  else if(!is.na(df_1)){
    # we go through partial eta
    n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
    partial_eta=(val*df_1)/(val*df_1+df_2)
    d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
  }
  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "beta"=NA, "SE"=NA))
}
```

```{r}
parse_chisq <- function(chival, within_between){
  df=str_extract(chival, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  n=str_extract(chival, ",N=.*\\)") |> str_sub(4,-2) |> as.numeric()
  val=str_extract(chival, "\\)=.*") |> str_sub(3,-1) |> as.numeric() |> abs()
  pval=pchisq(val,df, lower.tail=F)
  phi=sqrt(val/n)
  d_calc=NA
  if (!is.na(df)&&df==1){
    d_calc=esc_phi(phi,pval,n, es.type="d")$es
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=n, "beta"=NA, "SE"=NA))
}

@@

```{r}
parse_mean_ci <- function(mci,within_between,n){
  cond1=str_extract(mci, "m1.*\\],")
  cond2=str_extract(mci, "m2.*\\]")
  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se1=high1-low1/(2*1.96)
  se2=high2-low2/(2*1.96)
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
}
```

```{r}
parse_mean_sd <- function(msd,within_between,n){
  cond1=str_extract(msd, "m1.*\\),")
  cond2=str_extract(msd, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  sd_pool=(sd1+sd2)/2
  se=sd_pool/sqrt(n)
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
}

@@

```{r}
parse_mean_se <- function(mse,within_between,n){
  cond1=str_extract(mse, "m1.*\\),")
  cond2=str_extract(mse, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
}

```{r}
parse_wilcoxon <- function(wilcox){
  z=str_sub(wilcox,11,-1) |> as.numeric()
  pval=pnorm(z,lower.tail=F)
  #r=z/sqrt(n)
  #d_calc=4*r/(sqrt(1-r**2))
  d_calc=NA
    return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))

}
```

parse_beta_se <- function(raw_stat){
    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
    zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
}

@@

parse_beta_ci <- function(raw_stat){
  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)
  zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
}

@@

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "beta"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="c"){return(parse_chisq(raw_stat, within_between))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_ci(raw_stat))}

>>>>

parse_t <- function(tval, within_between) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pt(q=val, df=df, lower.tail=FALSE)*2
  d_calc=NA
  N_from_df=NA
  if(within_between=="between"){
    d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
    N_from_df=df+2 # between so add 2
  }
  else{
    d_calc=val/sqrt(df)
    N_from_df=df+1
  }
  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
}
```

```{r}
parse_f <- function(fval, within_between){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
  d_calc=NA
  N_from_df=df_1+df_2+1
  if(!is.na(df_1)&&df_1==1){
    if(within_between=="between"){
      d_calc=2*sqrt(val)/sqrt(df_2) # if there's just two groups, then F=t**2 and we can use the t-test thingy
    }
    else{
      d_calc=sqrt(val)/sqrt(df_2)
    }
  }
  else if(!is.na(df_1)){
    # we go through partial eta
    n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
    partial_eta=(val*df_1)/(val*df_1+df_2)
    d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
  }
  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
}
```

```{r}
# for proportions 
#ex <- "prob: 13 / 14 , 2 / 14"
parse_prop <- function(propval){
  val <- str_extract_all(propval, "[0-9]+")[[1]]
  num1 <- val[1] |> as.numeric()
  den1 <- val[2] |> as.numeric()
  num2 <- val[3] |> as.numeric()
  den2 <- val[4] |> as.numeric()
  est1 <- num1/den1
  est1_var <- est1*(1-est1)/den1
  est2 <- num2/den2
  est2_var <- est2*(1-est2)/den2
  diff <- est1-est2
  diff_var <- est1_var+est2_var
  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
}
#parse_prop(ex)

@@

```{r}
parse_mean_ci <- function(mci,within_between,n){
  cond1=str_extract(mci, "m1.*\\],")
  cond2=str_extract(mci, "m2.*\\]")
  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se1=high1-low1/(2*1.96)
  se2=high2-low2/(2*1.96)
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=NA, "SE"=NA))
}
```

```{r}
parse_mean_sd <- function(msd,within_between,n){
  cond1=str_extract(msd, "m1.*\\),")
  cond2=str_extract(msd, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  sd_pool=(sd1+sd2)/2
  se=sd_pool/sqrt(n)
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=NA, "SE"=NA))
}

@@

```{r}
parse_mean_se <- function(mse,within_between,n){
  cond1=str_extract(mse, "m1.*\\),")
  cond2=str_extract(mse, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=NA, "SE"=NA))
}

@@

parse_beta_se <- function(raw_stat){
    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
    zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
}

@@

parse_beta_ci <- function(raw_stat){
  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)
  zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
}

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,4)=="prop"){return(parse_prop(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_ci(raw_stat))}
